---
title: "Homework_08"
author: "Ashley Lantigua"
date: "2023-03-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating Fake Data Sets To Explore Hypothesis

## 1. Acquiring Data from a paper 
  
  # I acquired data from the paper Song et. al, 2019, "Brachypodium histone deacetylase BdHD1 positively regulates ABA and drought stress responses" 
  # Data is from Figure 3b and 3c
  # This is looking at the growth in Length(cm) of a WT and bdhd1-30 mutant in the presence of Control and ABA. 
  # The Sample size is n=30 for each one 
  # Control       WT = 6.5  SD = 0.125
  # Control bdhd1-30 = 6    SD = 0.35
  # ABA           WT = 3.5  SD = 0.125
  # ABA     bdhd1-30 = 4.5  SD = 0.25
  
  #The pattern we will chose is a normal distribution 
  
## ANOVA set up

```{r}
#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 4

#Name of Groups 
  nName <- c("Control-WT", "ABA-WT" )
  
#Number of Observations in each group
  nSize <- c(30, 30)
  
#Mean of each group
  nMean <- c(6.5, 3.5)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2])) 
             
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  aggregate(resVar~TGroup,data=ANOdata,FUN = mean)
  #unlist(z)
  #z
  #unlist(z)[7]
  ANOsum <- list(Fval = unlist(z)[7], 
                 probF = unlist(z)[9])
  ANOsum
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,
                    aes(x=TGroup,
                        y=resVar,
                        fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")

```

## Running analysis multiple times 

# Run number 1

```{r}

#Run number 1 

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(30, 30)
  
#Mean of each group
  nMean <- c(6.5, 3.5)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")
  
```
  

# Run number 2 
  
```{r}
  #Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(30, 30)
  
#Mean of each group
  nMean <- c(6.5, 3.5)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")

```

# Run Number 3

```{r}

  #Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(30, 30)
  
#Mean of each group
  nMean <- c(6.5, 3.5)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")

```


## Trying out different means and differences between the groups 

# Testing difference of 1

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(30, 30)
  
#Mean of each group
  nMean <- c(6.5, 5.5)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")

```



# Testing difference of 0.5

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(30, 30)
  
#Mean of each group
  nMean <- c(6.5, 6)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")





```

# Testing difference of 0.05

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(30, 30)
  
#Mean of each group
  nMean <- c(6.5, 6.45)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")





```


# Testing difference of 0.06

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(30, 30)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")





```

# For the means, the smallest the difference can be that it can be considered significant (p < 0.05) is 0.06. This is quite a small number. 



## With the Effect Size chosen, what is the minimum sample size would need to be statistically significant 

# Testing sample size of 50

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(50, 50)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")



```


# Testing sample size of 40

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(40, 40)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")



```


# Testing sample size of 35

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(35, 35)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")



```

# Testing sample size of 37

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(37, 37)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")



```


# Testing sample size of 36

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(36, 36)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)
  
#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")



```



# The smallest sample size needed to get a significant differences is a sample size of 35. 


## Running the randomization two more times 

# Run 1

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(37, 37)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)

#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")



```


# Run 2

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(37, 37)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)

#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")



```


# run 3

```{r}

#Loading  ggplot2

  library(ggplot2)

#Number of treatment groups 
  nGroup <- 2

#Name of Groups 
  nName <- c("Control", "ABA")
  
#Number of Observations in each group
  nSize <- c(37, 37)
  
#Mean of each group
  nMean <- c(6.5, 6.44)
  
#Standard Deviation of each group
  nSD <- c(0.125, 0.125)

#ID vector for each row
  
  ID <- 1:(sum(nSize))
  resVar <- c(rnorm(n=nSize[1], mean=nMean[1], sd=nSD[1]),
              rnorm(n=nSize[2], mean=nMean[2], sd=nSD[2]))
  TGroup <- rep(nName, nSize)
  ANOdata <- data.frame(ID,TGroup,resVar)
  str(ANOdata)
  
#Plotting ANOVA data
  
  ANOplot <- ggplot(data=ANOdata,aes(x=TGroup, y=resVar, FILL=TGroup)) + 
             geom_boxplot()
  print(ANOplot)

#Modeling ANOVA data

  ANOmodel <- aov(resVar~TGroup, data = ANOdata)
  print(ANOmodel)
  print(summary(ANOmodel))
  z <- summary(ANOmodel)
  str(z)
  
#Basic ggplot of ANOVA data
  
  ANOPlot <- ggplot(data=ANOdata,aes(x=TGroup,y=resVar,fill=TGroup)) +
           geom_boxplot()
  print(ANOPlot)
# ggsave(filename="Plot2.pdf",plot=ANOPlot,device="pdf")



```


# When looking at the randomization every so often sometimes you get a p value that is not statistically significant. 