---
title: "Homework #6"
author: "Ashley Lantigua"
date: "2023-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 Examining the Iris data set
```{r}
#loading the packages 
library(dplyr)
library(tidyverse)

#cleaning the data

irisClean <- iris[complete.cases(iris[,]),]

#examining the iris dataset
str(iris)
str(irisClean)

```


## 2 Creating a new data frame that only contains the species virginica and versicolor 
 #sepal lengths longer than 6 cm
 #sepal widths longer than 2.5
```{r}

##loading the packages 
library(dplyr)
library(tidyverse)

#creating the new data frame 

iris1 <- filter(irisClean, Species %in% c("virginica", "versicolor") & Sepal.Length > 6 & Sepal.Width > 2.5)

#examining the data frame 

head(iris1)


```

There are 28 observations that fit this criteria and 5 variables

## 3 Now create a iris2 data frame that only contains the columns for Species, Sepal.Length, and Sepal.Width

```{r}
##loading the packages 
library(dplyr)
library(tidyverse)

#selecting for the Species, Sepal.Length, and Sepal.Width

iris2 <- select(iris1, Species, Sepal.Length, Sepal.Width)

str(iris2)

```

There are 28 observations and 3 variables. 

##4 Create an iris3 data frame from iris 2 that orders the observations from largest to smallest sepal length. 

```{r}
##loading the packages 
library(dplyr)
library(tidyverse)

#creating the new data frame 

iris3 <- arrange(iris2, by= desc(Sepal.Length))

#showing the first 6 rows 

head(iris3, 6)


```


## 5. Create a new data frame that creates a column with a sepal area value 

```{r}
##loading the packages 
library(dplyr)
library(tidyverse)

#creating the data frame 

iris4 <- mutate(iris3, Sepal.Area=Sepal.Length*Sepal.Width)

#observing the data frame 
str(iris4)

```
There are 28 observations and 4 variables 

## 6. Create a function that calculates the average sepal length, the average sepal width and the sample size of the entire iris4 data frame and print iris5

```{r}

#creating function that calculates avg sepal length, sepal width and sample size for entire iris4 data

iris5 <- summarize(iris4, average_sepal_length = mean(Sepal.Length),
  average_sepal_width = mean(Sepal.Width), number = n())

print(iris5)

```

## Create a function that Create a function that calculates the average sepal length, the average sepal width and the sample size for each species and print iris5

```{r}

#creating function 

iris_by_species <- group_by(iris4, Species)

iris6 <- summarize(iris4, average_sepal_length = mean(Sepal.Length),
  average_sepal_width = mean(Sepal.Width), number = n())

print(iris6)

```


## Piping the whole thing

```{r}

library(dplyr)
library(tidyverse)
library(magrittr)

irisFinal <-  irisClean %>% filter(Species== c("virginica","versicolor") & Sepal.Length > 6 & Sepal.Width > 2.5) %>% 
  select(Species, Sepal.Length, Sepal.Width) %>% 
  arrange(by= desc(Sepal.Length)) %>% 
  mutate(Sepal.Area=Sepal.Length*Sepal.Width) %>% 
  group_by(Species) %>%
  summarize(average_sepal_length = mean(Sepal.Length), average_sepal_width = mean(Sepal.Width), number = n())

print(irisFinal)

```


## Making the data long form 

```{r}
#making the data long form 

longform_iris <- iris %>% 
  pivot_longer(cols= Sepal.Length:Petal.Width, 
  names_to = "Measure", 
  values_to = "Value", 
  values_drop_na = T)

print(longform_iris)

```

