---
title: "Homework_7"
author: "Ashley Lantigua"
date: "2023-04-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Used for this experiment

## Paper: Root Trait Responses to Drought Are More Heterogenous than Leaf Trait Responses 
## Link: https://besjournals.onlinelibrary.wiley.com/doi/epdf/10.1111/1365-2435.13656
## Data: https://datadryad.org/stash/dataset/doi:10.5061%2Fdryad.4f4qrfj91

## Open Libraries and Read in Data Vector

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

#read the data csv

#z <- read.table("MyDataFile.csv",header=TRUE,sep=",")
#str(z)
#summary(z)

# quick and dirty, a truncated normal distribution to work on the solution set

z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)
names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)

```

## Plot Histogram of Data 

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)

```


## Plot Histogram of Data

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

```

## Get Maximum Likelihood Parameters for Normal

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

normPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute

```

## Plot Normal Probability Density

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat

```

## Plot Exponential Probability Density

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2
 
```
 
## Plot Uniform Probability Density

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3
 
```


## Plot Gamma Probability Density 

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
 
```

## Plot Beta Proability Density

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial

```


## Questions: 

# How do the two histogram profiles compare? Do you think the model is doing a good job of # # simulating realistic data that match your original measurements? Why or why not?

# If you have entered a large data frame with many columns, try running all of the code on a different variable to see how the simulation performs.



