---
title: "Homework_7"
author: "Ashley Lantigua"
date: "2023-04-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 and 2: Running the given data and my chosen data 
    ## Find the best-fitting distribution
## Data Used for this experiment

## Paper: Root Trait Responses to Drought Are More Heterogenous than Leaf Trait Responses 
## Link: https://besjournals.onlinelibrary.wiley.com/doi/epdf/10.1111/1365-2435.13656
## Data: https://datadryad.org/stash/dataset/doi:10.5061%2Fdryad.4f4qrfj91

## Open Libraries and Read in Data Vector

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
library(tidyr)

#read the data csv
  
  

  setwd("~/BIO381")

  shootmass <- read.table("traits_25grasslands.csv",header=TRUE,sep=",")
  
  shootmass <- shootmass$shootmass
 
  str(shootmass)

  
 #str(shootmass)
  
  
#summary(z)

# quick and dirty, a truncated normal distribution to work on the solution set

  #z <- rnorm(n=3000,mean=0.2)
  shootmass <- data.frame(1:236,shootmass)
  shootmass <- shootmass %>% drop_na()
  
  str(shootmass)
  
  names(shootmass) <- list("ID","myVar")
  shootmass <- shootmass[shootmass$myVar>0,]
  shootmass <- shootmass %>% drop_na()
  
  str(shootmass)
  summary(shootmass$myVar)

```

## Plot Histogram of Data 

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

p1 <- ggplot(data=shootmass, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)

```


## Plot Histogram of Data

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

```

## Get Maximum Likelihood Parameters for Normal

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

normPars <- fitdistr(shootmass$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute

```

## Plot Normal Probability Density

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(shootmass$myVar),len=length(shootmass$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(shootmass$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat

```

## Plot Exponential Probability Density

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

expoPars <- fitdistr(shootmass$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(shootmass$myVar), args = list(rate=rateML))
 p1 + stat + stat2
 
```
 
## Plot Uniform Probability Density

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(shootmass$myVar), args = list(min=min(shootmass$myVar), max=max(shootmass$myVar)))
 p1 + stat + stat2 + stat3
 
```


## Plot Gamma Probability Density 

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
#library(fitdistrplus)


gammaPars <- fitdistr(shootmass$myVar,"gamma", lower=c(0.00105,0.00105))

shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(shootmass$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
 
```

## Plot Beta Proability Density

```{r}

library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

#pSpecial <- ggplot(data=shootmass, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  #geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  #xlim(c(0,1)) +
  #geom_density(size=0.75,linetype="dotted")

#betaPars <- fitdistr(x=shootmass$myVar/max(shootmass$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
#shape1ML <- betaPars$estimate["shape1"]
#shape2ML <- betaPars$estimate["shape2"]

#statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(shootmass$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
#pSpecial + statSpecial

```

## 3: Simulate data and 


```{r}

# now do the same for a gamma distribution, which has a shape and rate parameter as outputs from fitdistr

  gammaPars <- fitdistr(shootmass$myVar,"gamma", lower=c(0.00105,0.00105))

shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]
  
   z<- fitdistr(shootmass$myVar,"gamma",lower=c(0.00105,0.00105))
   
   print(z)

  shapeML <- z$estimate["shape"]
  rateML <- z$estimate["rate"]
  
  
  g_sim <- rgamma(n=236, shape = shapeML, rate = rateML)
  
  str(g_sim)
  
    g_sim <- data.frame(1:236,g_sim)
    
    str(g_sim)
  
    g_sim <- g_sim %>% drop_na()
  
    str(g_sim)
  
    names(g_sim) <- list("id","myVar")
  #g_density <- dgamma(x=, shape = shapeML, scale = rateML)
#qplot(x,g_density,geom="line") + annotate(geom="point",x=frog_data,y=0.001,color="red")  
  
  g_sim_hist <- ggplot(data=g_sim, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) +
     geom_line(aes(x=myVar, y=dgamma(myVar, shape = shapeML, rate = rateML)), color="red", size = 1) +
    scale_x_continuous(limits = c(0,25000), breaks = c(5000, 10000, 15000, 20000, 25000))
    
     
    #stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(g_sim$myVar), args = list(shape=shapeML, rate=rateML))
    
  
  
  plot(g_sim_hist)
  

  p1 + stat4
 
  #plot(density(g_sim)) 
  
  #plot(g_density)
  
  


# plot the density function for the gamma and annotate the plot with the original data

#g_density <- dgamma(x=x,shape=z$estimate["shape"],rate=z$estimate["rate"])
#qplot(x,g_density,geom="line") + annotate(geom="point",x=frog_data,y=0.001,color="red")   

```


## Questions: 

## How do the two histogram profiles compare?

### The two histogram profiles have the same shape and range.

## Do you think the model is doing a good job of simulating realistic data that match your original measurements? Why or why not?

### The model does a good job of simulating the original data, as the shape and range are similar. 




