---
title: "Homework_10"
author: "Ashley Lantigua"
date: "2023-04-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## For Loops and Randomization Tests

## 1. Using a for loop, write a function to calculate the number of zeros in a numeric vector

```{r}
#creating the function with a for loop

zero_vector <- round(runif(25, min = 0, max = 1), 0)

print(zero_vector)

count_zero <- function(vector) {
  counter <- 0
for (i in seq_along(vector)) {
    if (vector[i] == 0) next
  counter <- counter + 1
  }
return(counter)
}

count_zero(zero_vector)
```

## 2. Use subsetting instead of a loop to rewrite the function as a single line of code 

```{r}
#Using subsetting 

zero_vector <- round(runif(25, min = 0, max = 1), 0)

zero_vector_count <- sum(zero_vector == 0)

print(zero_vector_count)

```


## 3. Function that takes two inputs and creates a matrix that of the dimensions and each elemetn is the product of the row number and the column number

```{r}

product_matrix <- function(row, column) {
  total <- row * column
  amount <- rep(0, total)
  m <- matrix(amount, nrow = row)
  for (i in 1:nrow(m)) {
    for (j in 1:ncol(m)) {
      m[i,j] <- i * j
    }
  }
  return(m)
}

product_matrix(row = 5, column = 5)

product_matrix(row = 3, column = 2)

```

## 4. Randomization Tests 

## a. Simulate a dataset with 3 groups of data 
        # create a dataframe that has one column for the group and one column for the response variable 
        
```{r}

library(ggplot2)
library(dplyr)

set.seed(100)

#creating the groups 

group_num <- c(rep("Group_1",6), rep("Group_2", 6), rep("Group_3", 6)) 

print(group_num)

#create response variable

z <- c(runif(6, min = 0, max = 25), runif(6, min = 0, max = 25), runif(6, min = 0, max = 25))

z <- as.numeric(z)

print(z)

#combine into a dataframe 

df <- data.frame(Group = group_num, Response = z )

print(df)

df <- as.data.frame(df)

# Creating Meansum function 

##############################
# FUNCTION: meansum
# purpose: Will calculate the mean sum by group
# input: the data frame
# output: a data frame with a summary of the mean
#-------------------- 
meansum <- function(df) {

output <- aggregate(df$Response, list(df$Group), FUN=mean)

colnames(output) <- c("Group", "Means")

print(output)

}

# Trying the function

  
meansum(df)


```

## b. Write Function that reshuffles the response variable and calculates the mean of each group

```{r}

#Reshuffles the Response variable 

##############################
# FUNCTION: reshuffle and calc mean
# purpose: to reshuffle the column and calulate the mean
# input: the data frame
# output: the mean for each group 
#-------------------- 
shuffle_mean <- function(df) {
  
  df <- transform( df, Response = sample(Response))
  
  output <- aggregate(df$Response, list(df$Group), FUN=mean)

colnames(output) <- c("Group", "Means")

  print(output$Means)

}


## Testing the new function that shuffles and creates a vector with the means


 firstshuffle <- shuffle_mean(df)

 secondshuffle <- shuffle_mean(df)


 firstshuffle
 
 secondshuffle
 
```


## c. Use a loop to repeat the function in b 100 times. 


```{r}


#Loading packages 

  library(dplyr)

#Prepping for the loop

    loopreplicate <- 1:100
  
    #shufflelist <- list()
    
    #shufflelist <- vector("list", length = 100)
   
    shuffle_df <- expand.grid(rep = loopreplicate)
    shuffle_df$Group1 <- NA
    shuffle_df$Group2 <- NA
    shuffle_df$Group3 <- NA
    
    str(shuffle_df)
    
    
# For loop to repeat the function 100 times 
 
  for (i in 1:nrow(shuffle_df)) {
    
    shuffle <- shuffle_mean(df)
    shuffle_df[i,c(2,3,4)] <- shuffle
 
    
  }

    
#four columns, replicate#, group mean 1, group mean 2, group mean 3 
    
    #check the data frame
    
    str(shuffle_df)
    

```

## d. Create a histogram that will plot the reshuffle means 

```{r}

library(ggplot2)


  #Group 1 histogram

  Group1_hist <- ggplot(data=shuffle_df, aes(x=Group1, y=..density..)) +
  geom_histogram(color="grey60",fill="pink", linewidth=0.2) +
    theme_classic()

  plot(Group1_hist)

    #Group 2 histogram

  Group2_hist <- ggplot(data=shuffle_df, aes(x=Group2, y=..density..)) +
  geom_histogram(color="grey60",fill="lightblue", linewidth=0.2) +
    theme_classic()
  
     plot(Group2_hist)
  
    #Group 3 histogram

  Group3_hist <- ggplot(data=shuffle_df, aes(x=Group3, y=..density..)) +
  geom_histogram(color="grey60",fill="lightgreen", linewidth=0.2) +
    theme_classic()

  plot(Group3_hist)
  
```

## Creating a combined histogram plot

```{r}

library(ggplot2)
library(tidyr)


Group1 <- data.frame( Means = shuffle_df$Group1)

Group2 <- data.frame( Means = shuffle_df$Group2)

Group3 <- data.frame( Means = shuffle_df$Group3)

str(Group1)

CombinedData <- rbind (Group1, Group2, Group3)

str(CombinedData)


new_plot <- ggplot(CombinedData, aes(x= Means)) + geom_histogram(data = Group1, fill = "pink", alpha = 0.9) + geom_histogram(data = Group2, fill = "lightblue", alpha = 0.5)+ geom_histogram(data = Group3, fill = "lightgreen", alpha = 0.3)

plot(new_plot)


```

They appear to be a normal distribution! 

