---
title: "Homework_10"
author: "Ashley Lantigua"
date: "2023-04-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## For Loops and Randomization Tests

## 1. Using a for loop, write a function to calculate the number of zeros in a numeric vector

```{r}
#creating the function with a for loop

zero_vector <- round(runif(25, min = 0, max = 1), 0)

print(zero_vector)

count_zero <- function(vector) {
  counter <- 0
for (i in seq_along(vector)) {
    if (vector[i] == 0) next
  counter <- counter + 1
  }
return(counter)
}

count_zero(zero_vector)
```

## 2. Use subsetting instead of a loop to rewrite the function as a single line of code 

```{r}
#Using subsetting 

zero_vector <- round(runif(25, min = 0, max = 1), 0)

zero_vector_count <- sum(zero_vector == 0)

print(zero_vector_count)

```


## 3. Function that takes two inputs and creates a matrix that of the dimensions and each elemetn is the product of the row number and the column number

```{r}

product_matrix <- function(row, column) {
  total <- row * column
  amount <- rep(0, total)
  m <- matrix(amount, nrow = row)
  for (i in 1:nrow(m)) {
    for (j in 1:ncol(m)) {
      m[i,j] <- i * j
    }
  }
  return(m)
}

product_matrix(row = 5, column = 5)

product_matrix(row = 3, column = 2)

```

## 4. Randomization Tests 

## a. Simulate a dataset with 3 groups of data 
        # create a dataframe that has one column for the group and one column for the response variable 
        
```{r}

library(ggplot2)
set.seed(100)

#creating the groups 

group_num <- c(rep("Group_1",6), rep("Group_2", 6), rep("Group_3", 6)) 

print(group_num)

#create response variable

z <- c(runif(6, min = 0, max = 25), runif(6, min = 0, max = 25), runif(6, min = 0, max = 25))

z <- as.numeric(z)

print(z)

#combine into a dataframe 

df <- data.frame(Group = group_num, Response = z )

print(df)

```

## b. Write Function that reshuffles the response variable and calculates the mean of each group

```{r}

#Reshuffles the Response variable 

#Calculates the mean 

  means <- tapply(df$Group, df$Response, mean)
  print(means)

# Stores the means in a vector of length 3 



```


## c. Use a loop to repeat the function in b 100 times. 


```{r}

# For loop to repeat the function 100 times 
# it will store results in a dataframe
# Replicate numbers, and the three group means 


```

## d. Create a histogram that will plot after each reshuffle 

```{r}



```


