---
title: "Homework_11"
author: "Ashley Lantigua"
date: "2023-05-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Batch Processing of the DEG overlap documents 


```{r}
  
#Setting Working Directory 
  
  
  setwd("~/BIO381/LantiguaBio381/VennDiagram_Results")
  getwd()
  
  #library
    
  library(mgsub)
  library(stringr)
  library(purrr)
  library(tidyverse)
  library(data.table)
  library(magrittr)
  library(stringr)
  library(mygene)
  library(dplyr)

#Start the function 

 ##############################
 # FUNCTION: DESeq Batch Process
 # purpose: To take in files with a list of genes and convert them to the correct nomeclature and output a csv file that has the converted 
 # input: The File Folder, The number of files 
 # output: A CSV file
 #-------------------- 
 DESeq_Batch_Process <- function(file_folder) {


#Setting Variables in the Loop 
  
  #file_number <- 9
  
  
  csvfiles <- list.files(file_folder)
  print(csvfiles)
  
  str(csvfiles)
  
  csv_names <- mgsub(csvfiles, c("./",".csv"), c("",""))

 
#Loop #1 - DNA loop 
  
  #Create loop names 
  
  
   dat <- list()
  
  csvdata <- for(i in seq_along(csvfiles)){
       data <- read.table(file= paste(file_folder, csvfiles[i],sep=""),
                     sep=",",
                     header=TRUE) 
                    
  }
  
  
  
  #csvdata <- lapply(csvfiles, FUN = fread(x)) %>%
  #set_names(dataframe_names)
  

  #csvdata <- lapply(csvfiles, FUN = fread(x)) %>%
  #set_names(dataframe_names)
  
  
  for (i in seq_along(csvdata)) {
    
    #Choosing the DNA of the list 
    

  #filter rows that contain the string 'Guard' in the player column
    DNA_DEG_List_[i] <- csvdata[[i]] %>% dyplyr::filter(grepl("gene-"))
    #DNA_DEG_List_1 <- csvdata[[1]] %>% dyplyr::filter(grepl("gene-"))
    
    #DNA_DEG_List_[i] <- csvdata[[i]][str_detect(csvdata[[i]], "gene-")]

    #filter rows that contain the string 'Guard' in the player column

    #DNA_DEG_List_[i] <- csvdata[[i]] %>% filter(grepl("gene-"))
    
    DNA_DEG_List_[i] <- str_replace(DNA_DEG_List_[i], "gene-", "")
  
  }
  
   
  
#Loop #2 - DNA loop 
  

    for (i in seq_along(csvdata)) {
    
    #Choosing the DNA of the list 
      
     RNA_DEG_List_[i] <- csvdata[[i]] %>% dyplyr::filter(grepl("rna-"))
    
     #RNA_DEG_List_[i] <- csvdata[[i]][str_detect(csvdata[[i]], "rna-")]
    
    RNA_DEG_List_[i] <- str_replace(RNA_DEG_List_[i], "rna-", "")
  
    }
 }
  
  #DESeq_Batch_Process("~/BIO381/LantiguaBio381/VennDiagram_Results/")
  
```

## Ran into issues with this batch code because the read.table function wasn't working. I kept getting this error code. 

 # Error in data[i] <- read.table(file = paste(file_folder, csvfiles[i],  : 
  object of type 'closure' is not subsettable





## Some old code I was working on that I would have added if it read the files and the package I was trying to use. 


```{r}

      

  #close loop 
  
  #for (i in seq_len(file_number)) {
    
    #DNA_DEG_List
    
  #  DNA_DEG_List_[i] <- (DNA_DEG_List_[i], scopes = "symbol", fields = "ensembl.gene", return.as = "DataFrame")
    
    #Remove rows with NAs
    
    #DNA_DEG_List_[i] <- DNA_DEG_List_[i][complete.cases(DNA_DEG_List_[i]),]
    
    #RNA_DEG_List                             
                                 
    #RNA_DEG_List_[i] <- queryMany(RNA_DEG_List_[i], scopes = "refseq", fields = "ensembl.gene", return.as = "DataFrame")
    
  
  
    #Remove rows with NAs
  
     #RNA_DEG_List_[i] <- RNA_DEG_List_[i][complete.cases(RNA_DEG_List_[i]),]
    

#Combine the objects 

    #combine the RNA and DNA 

    #  DEG_List_[i] <- c(DNA_DEG_List_[i], RNA_DEG_List[i])

    #combine the data object for each one into one data frame
      
     # DEG_List_df <- rbind(DEG_List_df, DEG_List_[i])
      
 #}

#save into a csv
      
      # write.table(x= DEG_List_df, file="DEG_List_df.CSV", sep = ",", row.names = FALSE)
       
      # str(DEG_List_df)



```